Computer Science House By-Laws

### 2016-11-10 bylaws.tex
Oops. Fixed*
Fixed better.

At any point before the Introductory Evaluation, an Introductory Member may make a second attempt at the Introductory Packet by requesting a new Introductory Packet from the Evaluations Director. The results of the new Introductory Packet may only affect the number of signatures evaluated at the Introductory Evaluation and, as long as the Introductory Member receives the appropriate number of packet signatures that would normally be required in the \ref{Creation of Accounts} process. 

>>>>

At any point before the Introductory Evaluation, an Introductory Member may make a second attempt at the Introductory Packet by requesting a new Introductory Packet from the Evaluations Director. Then, the Introductory Member goes through the \ref{Creation of Accounts} proccess once again. The results of the new Introductory Packet will also affect the number of signatures evaluated at the Introductory Evaluations. 
